---
title: "SKAT with custom weights"
author: "Tiffany Timbers"
date: "August 22, 2015"
output: html_document
---

## Optional add-on - apply custom weights to variants

### Create a custom weights file to assign weights to each variant

With SKAT we can choose to weight all variants equally, or give higher weights to rare variants as opposed to common 
variants, but we can also use custom variants, taking advantage *a priori* information about the type/severity of
mutation. For example, we would expect knockout mutations (*e.g.* nonsense, frameshifitng indels and splicing mutations)
to result in a more severe phenotype/disease outcome compared to a inframe deletion or missense mutation. These weights
can be chosen by the user, or they can be calculated using available tools such as SIFT (Kumar *et al., Nature Protocols*, 
2009) or Polyphen (Ramensky *et al., Nucleic Acids Research*, 2002).
```{r}
# R
# use reduced_SSID to get only the rows from gene_variants we will be performing SKAT on
head(reduced_SSID)
head(gene_variants)

# give gene_variants better column names
colnames(gene_variants) <- c("CHR", "POS", "variant", "REF", "ALT", "QUAL", "FILTER", "INFO")
reduced_gene_variants <- semi_join(gene_variants, reduced_SSID)
dim(gene_variants)
dim(reduced_gene_variants)

# get SIFT weigths from Mike or provide my file
```

### Apply SKAT and mutliple testing correction
```{r}
# R
## some r code to do this
```


